Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-06 paper/paper.tex
[paper] added latency results

\par The are some performance evaluation of Apache Spark and Apache Flink and other framework such as Yahoo Streaming Benchmark \cite{yahoo}. We believe that we still need to carry our evaluation for two reasons: \begin{enumerate*}[label=(\roman*)]
\item both frameworks are continuously improving in short time 
\item we aim to study the performance of some complex operations such as \texttt{groupByKey} \& \texttt{keyBy} in Apache Spark and Apache Flink, respectively.
\end{enumerate*}

@@

\par We consider the time delay between the streaming time of record in Kafka and the 
finish processing time in a workload as the platform's processing latency (measured in milliseconds). On the other hand, the number of processed stream's records (aircrafts position messages) per second within each streaming workload is the throughput measure. Since the Spark Streaming is micro-batch based,  We examine the effect of different batch intervals
of the Spark Streaming on the performance measurements.
\subsection{Latency Measurements}

@@

\end{subfigure}
\caption{Latency Results}
\label{fig:fig}
\end{figure}
\subsection{Throughput Measurements}

>>>>

\par The are some performance evaluation of Apache Spark and Apache Flink  such as Yahoo Streaming Benchmark \cite{yahoo}. We believe that we still need to carry our evaluation for two reasons: \begin{enumerate*}[label=(\roman*)]
\item both frameworks are continuously improving in short time 
\item we aim to study the performance of some complex operations such as \texttt{groupByKey} \& \texttt{keyBy} in Apache Spark and Apache Flink, respectively.
\end{enumerate*}

@@

\par We consider the time delay between the streaming time of record in Kafka and the 
finish processing time in a workload as the platform's processing latency (measured in milliseconds). On the other hand, the number of processed stream's records (aircrafts position messages) per second within each streaming workload is the throughput measure. Since the Spark Streaming is micro-batch based,  We examine the effect of different batch intervals
of the Spark Streaming on the performance measurements.
\subsection{Latency Results}

Figure 5 shows the results of latency measurements of the streaming workloads in Spark and Flink. The observed values present the mean value of multiple trails and measurements. Measurements for different batch intervals are given in Spark Streaming,  if we decrease  will not get better latency but it is even getting  worse. Results show that Flink outperform Spark streaming in term of processing latency in the both evaluation workloads.

@@

\end{subfigure}
\caption{Latency Measurements}
\label{fig:fig}
\end{figure}
\subsection{Throughput Results}
